%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[5]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} \textit{\small #2} & \textit{#3} \\
    \textit{\small#4} & \textit{\small #5} \\
  \end{tabular*}
  \vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Zhao Liu} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:905314204536}{+267-466-8234}
    $|$
    \faAt \hspace{.5pt} \href{mailto:zhaoliu@sas.upenn.edu}{zhaoliu@sas.upenn.edu}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/mrzhaoliu}{LinkedIn}
    $|$
    % \faGlobe \hspace{.5pt} \href{https://mrzhaoliu.github.io}{Personal Website}
    % $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Philadelphia,+PA,+USA/}{Philadelphia, PA, USA}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Mines Paris - PSL}
      {(Dual Degree Program)}
      {Paris, France}
      {Post-Master in International Environmental Management Candidate}
      {Nov 2023 \textbf{--} Expected Aug 2024}
      
    \resumeEducationHeading
      {University of Pennsylvania}
      {(Dual Degree Program)}
      {Philadelphia, USA}
      {Master of Environmental Studies Candidate}
      {Aug 2022 \textbf{--} Expected Aug 2024}

    \resumeEducationHeading
      {University of Pennsylvania Carey Law School}
      {}
      {Philadelphia, USA}
      {Master in Law, focus on environmental law and energy policy}
      {Aug 2022 \textbf{--} Aug 2023}
          
    \resumeEducationHeading
      {Renmin University of China}
      {(Dual Degree Program)}
      {Beijing, China}
      {Bachelor of Economics}
      {Sep 2018 \textbf{--} Jun 2022}

     \resumeEducationHeading
      {KEDGE Business School}
      {(Dual Degree Program)}
      {Marseille, France}
      {Bachelor of Management and Commerce (Bac+3)}
      {Sep 2018 \textbf{--} Oct 2021}
      
  \resumeSubHeadingListEnd

%----------- Publications & Presentations -----------

\section{Publications \& Presentations}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

        \textbf{Zhao Liu}, “Social Enterprise and Impact Investing.” \textit{Introduction to Social Organization Development}, China Renmin University Press, 2023 (Accepted)
        
        \textbf{Zhao Liu}, Yaqian Xiao, Shiqi Lin, “Current Situation and Trend Analysis of China’s Charitable Trust.” \textit{Research Report on Social Impact Finance in China (No.2)}, Social Sciences Academic Press (China), 2023 (Accepted)
        
        \textbf{Zhao Liu}, “Decarbonizing Power Generation in Pennsylvania \textbf{--} A Roadmap Beyond RGGI." \textit{Student-Published Anthology of Research at Kleinman Magazine}, Kleinman Center for Energy Policy at University of Pennsylvania, 2023
        
        \textbf{Zhao Liu}, “Decarbonizing Power Generation in Pennsylvania \textbf{--} A Roadmap Beyond RGGI.” Poster Exhibition at Energy Week of the University of Pennsylvania, Philadelphia, PA, March 2023
        
        \textbf{Zhao Liu}, “From Bottled Water to Filtered Water: Save Money and Save the Earth.” Presentation at the Penn Grad Talks of the University of Pennsylvania, Philadelphia, PA, February 2023
        
        \textbf{Zhao Liu}, “Current Situation and Trend Analysis of China’s Charitable Trust.” \textit{Research Report on Social Impact Finance in China (No.1)}, China Social Sciences Academic Press (China), 2021 (China’s first social impact finance book)
        
        Fang Yan, \textbf{Zhao Liu}, “Shenzhen Corporate Social Responsibility Development Report (2018-2019).” : Shenzhen Philanthropy Development Report (2018-2019), Sun Yat-sen University Press, 2021
        
        Wen Li, Xinke Gu, \textbf{Zhao Liu}, Wenqi Hu, “A-Share Listed Company Poverty Alleviation Practice Report (2020).” \textit{A-Share Listed Company Sustainable Development Value Assessment Report (2020)}, China Social Sciences Academic Press, 2021 (China Soft Science Special Award Winner Report)

        \vspace{3pt}

    }}
  \resumeSubHeadingListEnd


%----------- RESEARCH & PROJECT EXPERIENCE -----------

\section{Research \& Project Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  


     \resumeSubheading
      {Energy Justice Lab (Indiana University \& University of Pennsylvania)}{Philadelphia, USA}
      {Research Assistant to Prof. Sanya Carley, co-director of the lab}{Sep 2023 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Conducted Web scraping and cleaning for utility disconnection data using Python, R and Tableau.}
            \resumeItem{Helped file public information requests for utility data.}
            \resumeItem{Helped maintain legal data on the utility disconnection dashboard.}
            \resumeItem{Helped improve the functionality of the dashboard through additional data gathering and more granular geographic resolution.}
        \resumeItemListEnd

     \resumeSubheading
      {Penn Center for Science, Sustainability and the Media (PCSSM)}{Philadelphia, USA}
      {Research Assistant to Dr. Joe Romm, a senior Research Fellow at PCSSM}{May 2023 \textbf{--} Aug 2023}
        \resumeItemListStart
            \resumeItem{Researched greenwashing of carbon offsets, published in the white paper \textit{Are carbon offsets unscalable, unjust, and unfixable—and a threat to the Paris Climate Agreement?}}
            \resumeItem{Analyzed the Paris Agreement goals and alignment of the top 10 global greenhouse gas emitters.}
        \resumeItemListEnd
        
     \resumeSubheading
      {Penn Impact Investing}{Philadelphia, USA}
      {Project Analyst, in collaboration with Apollo Global Management }{Jan 2023 \textbf{--} May 2023}
        \resumeItemListStart
            \resumeItem{Analyzed technology and challenges in industrial decarbonization with team.}
            \resumeItem{Identified potential investment targets, and conducted business, financial, and impact analysis with team.}
            \resumeItem{Presented research to the impact investment team of Apollo Global Management as a representative of the team.}
        \resumeItemListEnd
        
     \resumeSubheading
      {The Wharton School of the University of Pennsylvania}{Philadelphia, USA}
      {Research Assistant at Harris Family Alternative Investments Program}{Feb 2023 \textbf{--} May 2023}
        \resumeItemListStart
            \resumeItem{Conducted research and guest coordination for the preparation of the Wharton Global Allocators Summit.}
        \resumeItemListEnd
        
     \resumeSubheading
      {Environmental Law Project (ELP) at the University of Pennsylvania Carey}{Philadelphia, USA}
      {Endangered Species Act Project Member}{Feb 2023 \textbf{--} Apr 2023}
        \resumeItemListStart
            \resumeItem{Partnered with Delaware Riverkeeper Network to protect endangered Atlantic sturgeon in the Delaware River.}
            \resumeItem{Drafted a comprehensive 15-page policy memorandum \textit{Benefits of Critical Habitat Designation} with team.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- Professional EXPERIENCE -----------

\section{Professional Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {World Resources Institute}{Beijing, China}
      {Research Intern at China Sustainable Transition Center (Remote)}{Sep 2023 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Examined international just transition experiences, focusing on the U.S. Inflation Reduction Act.}
            \resumeItem{Evaluated the current state and pathways of ecology-oriented development in China.}
        \resumeItemListEnd
    \resumeSubheading
      {Turn Forward}{Philadelphia, USA}
      {Policy Fellow}{Jun 2023 \textbf{--} Aug 2023}
        \resumeItemListStart
            \resumeItem{\textbf{Policy Advocacy:} Engaged in policy advocacy, including drafting a comment for CEQ's Ocean Justice Strategy.}
            \resumeItem{\textbf{Policy Research:} Co-authored a comprehensive roadmap for scaling offshore wind beyond 100 GW in the U.S.}
            \resumeItem{\textbf{Policy Library Building:} Developed a comprehensive library of offshore wind cases, policies, and research.}
        \resumeItemListEnd
    
    \resumeSubheading
      {FOFWEEKLY}{Beijing, China}
      {Part-time Columnist \& Researcher (Remote)}{Apr 2021 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{\textbf{Report Writing:} Co-author of \textit{FOFWEEKLY China PE/VC Impact Investing Report}, responsible for research.}
            \resumeItem{\textbf{Article Writing:} Wrote 20+ articles about PE/VC, ESG investing, and FoF, reposted by China’s famous media.}
        \resumeItemListEnd
    

    \resumeSubheading
      {MiraclePlus (former Y Combinator China)}{Beijing, China}
      {Investment Analyst Intern, with Outstanding Contribution Award}{Jun 2021 \textbf{--} Sep 2021}
        \resumeItemListStart
            \resumeItem{\textbf{Industry Analysis:} Wrote 13 comprehensive reports on ESG, carbon-neutral, and energy industries.}
            \resumeItem{\textbf{Due Diligence:} Wrote six due diligence reports on energy storage, water purification, ESG, and energy projects.}
            \resumeItem{\textbf{Deal Sourcing:} Liaised with startups to pinpoint 167 potential deals for review, setting an organization record.}
            \resumeItem{\textbf{Lecture Courses:} “The Logic and Opportunities behind ESG” and “Deal Sourcing and Communication in VC”.}
        \resumeItemListEnd
        
    \resumeSubheading
      {Conseil Interprofessionnel des Vins de Provence (CIVP)}{Marseille, France}
      {Part-time Assistant}{Jan 2021 \textbf{--} Jun 2021}
        \resumeItemListStart
            \resumeItem{\textbf{Market Consulting:} Concluded a four-phase market study and marketing strategy consulting with the team.}
            \resumeItem{\textbf{Report Writing:} Co-author of 61-page wine market report: \textit{Étude de marché et formulation de stratégie marketing en Chine (Research on the Chinese market and market strategy planning for the wine industry).}}
        \resumeItemListEnd

    \resumeSubheading
      {Ernst \& Young}{Shanghai, China}
      {ESG Intern, Climate Change and Sustainability Services (CCaSS) Department}{Nov 2020 \textbf{--} Feb 2021}
        \resumeItemListStart
            \resumeItem{\textbf{Article Writing:} Authored two articles on carbon neutrality and ESG, featured on E\&Y’s social media.}
            \resumeItem{\textbf{ESG Consulting:} Supported MSCI ESG rating benchmarking, ESG structuring, and policy creation for 12 HKEX and NASDAQ-listed companies.}
            \resumeItem{\textbf{ESG Reporting:} Compiled 15 chapters covering environmental, social and governance topics in six ESG reports.}
        \resumeItemListEnd
        
     \resumeSubheading
        {China Alliance of Social Value Investment}{Shenzhen, China}
        {Research Management Trainee at Research Institute (Remote)}{Feb 2020 \textbf{--} Oct 2020}
        \resumeItemListStart
            \resumeItem{Collected and scored 7,222 data points based on 26 ESG key issues for the “SV99” ESG index.}
            \resumeItem{Analyzed the major ESG and sustainability index and standards to help optimize the “SV99” ESG index.}
            \resumeItem{Research team member of “Innovative Practice of Poverty Alleviation of CSI 300 Companies”.}
            \resumeItem{Assisted in global ESG policy research, which was published in the book \textit{International ESG Investment Policies, Regulations, and Practices" (2021).}}
            \resumeItem{Responsible for departmental administrative tasks includes research project progress management.}
        \resumeItemListEnd
        
  \resumeSubHeadingListEnd



%----------- LEADERSHIP EXPERIENCE -----------

\section{Leadership Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Chairman, Campus Student Employment \& Career Development Association}{ (led a 57-person team), Renmin University of China} \\ \vspace{3pt}
        \textbf{Board Member, KEDGE Alumni Shanghai}{, KEDGE Business School} \\ \vspace{3pt}
        \textbf{Co-founder and Vice Secretary-General, KEDGE Finance Club China}{, KEDGE Business School} \\ \vspace{3pt}
        \textbf{Co-founder and Head of Publicity, KEDGE Business School Anti-COVID19 Fund}{, KEDGE Business School} \\ \vspace{3pt}

    }}
  \resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Second Place, Law 2030 Competition}{, University of Pennsylvania Carey Law School} \\ \vspace{3pt}
        \textbf{Scholarship for Academic Progress}{, Renmin University of China} \\ \vspace{3pt}
        \textbf{Scholarship for Social Work and Volunteerism}{, Renmin University of China} \\ \vspace{3pt}
        \textbf{Scholarship for Outstanding Student Leader}{, Renmin University of China} \\ \vspace{3pt}
        \textbf{Advanced Individual Title in Anti-COVID-19 Volunteerism}{, Renmin University of China} \\ \vspace{3pt}
        \textbf{Outstanding Youth League Member}{ (Four times,  campus level), Renmin University of China} \\ \vspace{3pt}
        \textbf{Second Place (2/3,500), JD Future Cup}{, a national college student skills competition hosted by JD.com (Jingdong)} \\ \vspace{3pt}
        \textbf{Bronze Award, The 4th Hong Kong University Student Contemporary Design Award}{, Hong Kong Art \& Design Association, Hong Kong Academy of Art and Design} \\ \vspace{3pt}

    }}
  \resumeSubHeadingListEnd

%----------- Certificates -----------

\section{Certificates}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Organizational Leadership for Social Workers}{, University of Pennsylvania SP2 \textbf{--} Wharton Professional Certificate} \\ \vspace{3pt}
        \textbf{Sustainability and Climate Risk Certificate (SCR®)}{, Global Association of Risk Professionals (GARP)} \\ \vspace{3pt}
        \textbf{Legal Research Certificate for Law Students}{, LexisNexis} \\ \vspace{3pt}
        \textbf{The Securities Qualification Certificate (exam cleared)}{, Securities Association of China (SAC)} \\ \vspace{3pt}
        \textbf{China Social Finance Mini MBA Certificate}{, KEDGE Business School} \\ \vspace{3pt}
        \textbf{Philanthropy Management Certificate}, {China Global Philanthropy Institute (CGPI)} \\ \vspace{3pt}


    }}
  \resumeSubHeadingListEnd


%----------- SKILLS -----------

\section{Skills}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ Microsoft Office, R, Python, ArcGIS, Tableau, Adobe Creative Cloud (Photoshop, Illustrator, InDesign)} \\ \vspace{3pt}
        
        
        \textbf{Languages:}{ English (Fluent), Chinese (Native), French (Fluent)}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \small{\item{
        % \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}
        
        % \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
    % }}
  % \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
